\Title

### 2023-07-06 cover_letter/2023-07-07_coverletter.tex
$200$ test movies

 \noteRev{We thank the reviewer for his constructive comment. This encouraged us to extend our task from using natural-like textures to actual natural images. This was further extended by using biologically inspired eye movements. We have kept the use of the synthetic textures in order to assess the relevant image parameters that are relevant for motion detection and we have drawn the analogies of our model with that found in the neurophysiological and psychophysical literature. We have added subgraph inset to illustrate the changes in parameters to the generation of figures.}

@@

 \noteRev{The main differences with the previous study are in the task to solve (section 2.1) and in the analysis of the results. The response of the model is tested on different sets of motion cloud stimuli with a control of the parameters of such stimuli generation (section 3.2). Regarding the MLR model, main differences with the previous ones are reported in the methods (P8, L285).}

@@

 \noteRev{We removed these sections to have a more concise explanation of the model and focused on resolving the motion detection task. We hope the manuscript is now more concise and clear to the point.}

>>>>

 \noteRev{We thank the reviewer for his constructive comment. While keeping the same computationnal framework, this encouraged us to extend our task from using natural-like textures to actual natural images. This was further extended by using biologically inspired eye movements to generate dynamical scenes with known ground truth. We have kept the use of the synthetic textures in order to assess the relevant image parameters that are relevant for motion detection and we have drawn the analogies of our model with that found in the neurophysiological and psychophysical literature. We have added subgraph inset to illustrate the changes in parameters to the generation of figures.}

@@

 \noteRev{We have repeated the testing of our model using $200$ movies and report less variable estimates for the accuracy. Thanks for this suggestion.}

@@

 \noteRev{By extending the learning and testing of our model on this newly defined motion detection task, we hope to have provided with a more thorough exploration of the capabilities of our model. The comparison of accuracy was also performed on the synthetic textures dataset in order to provide with a direct comparison with biological observations.}
